### 2021-03-04 article/paper_eng.tex
finished abstract

\section*{Acknowledgments}
\small{This work was partially supported by the Russian Science Foundation (project № 20-79-10185) in the studying of inhibitory connections training and by the grant INSERT NAME in the part of comparison of concvoltional and locally connected achitectures.}

@@

The introduction of inhibitory connections (with negative weights) allows to achieve a better distinction of features learned by the neurons. In this work it is shown that learning competition relationships in a locally connected SNN potentially leads to higher pattern recognition accuracy due to the organization of competition and cooperation between groups of neurons.

>>>>

\section*{Acknowledgments}
\small{This work was partially supported by the Russian Science Foundation (project № 20-79-10185) in the studying of inhibitory connections training and by the grant INSERT NAME in the part of comparison of convolгtional and locally connected achitectures.}

@@

The introduction of inhibitory connections (with negative weights) allows to achieve a better distinction of features learned by the neurons. In this work it is shown that learning competition relationships in a locally connected (LC) SNN potentially leads to higher pattern recognition accuracy due to the organization of competition and cooperation between groups of neurons. It is also shown that the LC SNN produces better results than a convolutional SNN.
